\documentclass[10pt]{article}
\usepackage{charter}
\usepackage{fullpage}
\usepackage[colorlinks=false]{hyperref}
\usepackage{currvita}
\usepackage{fontspec}

% Biblatex
\usepackage[american]{babel}
\usepackage[babel]{csquotes}
\usepackage[style=ieee,
  citestyle=numeric-comp,
  uniquename=false,
  hyperref=true,
  backend=biber, 
  babel=hyphen, 
bibencoding=inputenc]{biblatex}
\addbibresource{pub.bib}



% Better for lists with 1-2 items and short descriptions
\newenvironment{sublist}{%
  \begin{list}{}{%
    \setlength{\itemsep}{0em}\setlength{\parsep}{0em}%
      \setlength{\topsep}{0em}\setlength{\parskip}{0em}%
  }%
}%
{ \end{list} }

% Better for lists with more than 2 items and/or long descriptions
\newenvironment{subbulletlist}{%
  \begin{list}{\labelitemii}{%
    \setlength{\topsep}{\itemsep}\setlength{\parskip}{\parsep}%
    }%
}%
{ \end{list} }

\pagestyle{empty}

\begin{document}

\newlength{\oldcvlabelwidth}
\newlength{\oldcvlabelsep}
\newlength{\oldtemp}

\begin{cv}{{\large Renliang Gu}\\
  {\normalsize Iowa State University, Electrical \& Computer Engineering\\
    Email: {\mdseries \href{mailto:renliang@iastate.edu} 
    {renliang@iastate.edu}}
    \hfill Phone: {\mdseries 515-509-0114}
    \hfill Web: {\mdseries \href{http://co3125-07.ece.iastate.edu/renliang/}
    {co3125-07.ece.iastate.edu/renliang/}}
  }
}

\setlength{\oldcvlabelwidth}{\cvlabelwidth}
\setlength{\oldcvlabelsep}{\cvlabelsep}

\setlength{\cvlabelwidth}{1em}

\begin{cvlist}{Research Interest}
\item Statistical Signal Processing, Convext Optimization and X-ray 
Computed Tomography Imaging
\end{cvlist}

\begin{cvlist}{Education}
\item \emph{Ph.D., Electrical \& Computer Engineering}, Iowa State 
  University, Aug.\ 2010 $\sim$ Fall 2015 (expected)
  Advisor: Aleksandar Dogand\v{z}i\'c\\
  (GPA: 3.94/4.0)
\item \emph{B.Eng. (Hons), School of Information Science and Technology} 
  (Study in \emph{Chien-Shiung Wu College \footnote{
    Chien-Shiung Wu College, named after the outstanding alumna, selects 
    only the best students to take the fundamental intensive courses in EE for 
    the first 2 years. Samuel C. C. Ting, Noble Prize laureate, is the dean in 
    honor of this college.
  }} for the first two years), Southeast University, Nanjing, Aug.  2005 
$\sim$ July 2009
\\(Overall GPA: 88.15/100, Major GPA: 90.75)
\end{cvlist}

\setlength{\cvlabelwidth}{0em}
\setlength{\cvlabelsep}{\labelsep}
\begin{cvlist}{Publications}
\item
\begin{itemize}\itemsep=0.25em
    \item \fullcite{GuDogandzic2013}
    \item \fullcite{DogandzicGuQiuQNDE11}
    \item \fullcite{dgq11}

    %\item First author of 7 peer-reviewed conference and journal
    %  papers, including outlets such as \textit{IEEE Transactions on
    %  Mobile Computing}, \textit{IEEE Infocom} (18\% acceptance rate),
    %  and \textit{IEEE International Conference on Distributed Computing
    %  Systems (ICDCS)} (13.8\% acceptance rate).  All publications and
    %  presentations are available at
    %  \href{http://www.crhc.uiuc.edu/~mjmille2/publications/}
    %  {www.crhc.uiuc.edu/$\sim$mjmille2/publications/}.
    %\item External reviewer for several conferences and \textit{IEEE
    %  Transactions} journals.
    %\item Author of several online HOWTO articles, including a
    %  Linux/Windows dual boot guide that averages over 200 unique page
    %  views per day.
    \item A. Hu, R. Gu and P. Fan, ``A File Encryption Method of USB Mobile 
    Storage Device'', \emph{State Intellectual Property Office of 
    P.R.China}, Patent \#: 200910183069.1, Jul. 2009.
  \end{itemize}
\end{cvlist}

\setlength{\cvlabelsep}{\oldcvlabelsep}
\setlength{\cvlabelwidth}{1em}
\begin{cvlist}{Thesis}
\item R. Gu, ``A File Encryption System for USB Memory Device based on 
  Embedded System of ARM9'', \emph{Bachelor of Engineering Thesis}, 
  Southeast University, Jul. 2009.
\end{cvlist}

\begin{cvlist}{Teaching Assistant}
\item EE 224: Signal and System I
  \setlength{\oldtemp}{\parskip}
  \setlength{\parskip}{-0.05em}
  \begin{itemize}\itemsep=0.05em
      \item Fall 2010 (Lab instructor, homework and lab report grader)
      \item Spring 2011 (Lab instructor, lab report grader)
    \end{itemize}
\end{cvlist}
\setlength{\parskip}{\oldtemp}


\setlength{\cvlabelwidth}{0em}
\setlength{\cvlabelsep}{\labelsep}
\begin{cvlist}{Technical Experience}
\item
\begin{itemize}\itemsep=0.25em
    \item R.~Gu, GMSK modulator and demodulator design for GSM base station 
      on FPGA platform, Nov. 2009 $\sim$ July 2010.
      %\\Implemented by Verilog

    \item R.~Gu, 10/100M Ethernet-FIFO Convertor IP Core Design, Jul.~2009 
      $\sim$ Sept.~2009.\\
      One part of GSM transceiver. I was in charge of FPGA module including 
      PCB designing and Ethernet-FIFO interface verilog coding. The project 
      is now available at Opencores.com.

    \item R. Gu, P. Fan and J. Zhang, General USB Security Guard with 
      Fingerprint Recognition, Jun.~2008 $\sim$ Aug.~2008.\\
      The first prize project in National Undergraduate Electronic Design 
      Contest. Fingerprint is used for identification processed in DSP and 
      FPGA is used to resolve USB protocol and encrypt/decrypt the data.
  \end{itemize}
\end{cvlist}

%Academic Activities
\begin{cvlist}{Extracurricular}
\item
\begin{itemize}\itemsep=0.25em
    \item Review ICASSP 2013 paper.
    \item Visit Aichi Institute of Technology as a member of SEU 
      delegation, Japan. Oct. 2008.
    \item Participate the Microsoft Research Asia Young Fellowship Summer 
      Camp, May 2008.
    \item Serve as the Minister of Ministry of Science \& Technology in the 
      Students’ Union of Chien-Shiung Wu College, Mar.~2007 $\sim$ 
      Mar.~2008.
  \end{itemize}
\end{cvlist}

\begin{cvlist}{Major Scholarship and Awards}
\item
\begin{itemize}\itemsep=0.25em
    \item First Prize, National Undergraduate Electronic Design Contest – 
      2008 Information Security Technology Invitational Contest, 
      Sept.~2008.
    \item Scholarship of China Aerospace Science and Technology Corporation 
      (CASC), Sept.~2008.
    \item President’s Scholarship of Southeast University, Dec.~2007.
  \end{itemize}
\end{cvlist}

\setlength{\cvlabelwidth}{\oldcvlabelwidth}
\setlength{\cvlabelsep}{\oldcvlabelsep}
\end{cv}
\end{document}

